The Spatial Distribution of Local Group Satellites in a Cosmological Context

### 2016-06-13 paper/ms.tex
mas referencias 2

MIRAR Wang et al. 2013 que busca MWlike planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos

@@

\item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
similarly unlikely around paired and isolated hosts":\\
They use the Elvis simulations to study the satellite population of
paired vs isolated galaxies.\\
Conclusion: The observed flattening and the observed orbital alignment
are each reproduced by only 0.2 to 2 per cent of paired and isolated
systems incorporating the obscuration of satellites by randomly
oriented galactic discs.\\
Simulation: Elvis\\
Gas: NO\\
Resolution : ?\\
Number of host halos: 24 paired and 24 isolated host halos (4800
analyzed realizations).\\
Planes: 0.2 to 2 per cent\\
co-rotation: 0.2 to 2 per cent\\
note: co-rotation and alignments together are only observed in ONE of
4800 realizations.\\
}
\end{itemize}

>>>>

MIRAR Wang et al. 2013 que busca MW-like planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos

@@

\item{ Pawlowski et al. 2014: "Co-orbiting planes of sub-halos are
similarly unlikely around paired and isolated hosts":\\
They use the Elvis simulations to study the satellite population of
paired vs isolated galaxies.\\
Conclusion: The observed flattening and the observed orbital alignment
are each reproduced by only 0.2 to 2 per cent of paired and isolated
systems incorporating the obscuration of satellites by randomly
oriented galactic discs.\\
Simulation: Elvis\\
Gas: NO\\
Resolution : ?\\
Number of host halos: 24 paired and 24 isolated host halos (4800
analyzed realizations).\\
Planes: 0.2 to 2 per cent\\
co-rotation: 0.2 to 2 per cent\\
note: co-rotation and alignments together are only observed in ONE of
4800 realizations.\\
}

\item{Buck et al 2015 "EVIDENCE FOR EARLY FILAMENTARY ACCRETION FROM THE ANDROMEDA GALAXY'S THIN PLANE
OF SATELLITES":\\
They use zoom in cosmological simulations to study the possible formation of thin planes of satellite galaxies.\\
Conclusion: "We show that it is possible to obtain a thin, extended, rotating plane of satellites resembling the one in
Andromeda in cosmological collisionless simulations based on the Cold Dark Matter model. Our new
high resolution simulations show a correlation between the formation time of the dark matter halo
and the thickness of the plane of satellites." (...) "Our high resolution simulations show a correlation between the formation time of the dark matter halo
and the thickness of the plane of satellites. Our simulations have a high incidence of satellite planes
as thin, extended, and as rich as the one in Andromeda and with a very coherent kinematic structure
when we select high concentration/early forming halos."\\
Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
(7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
Gas: NO\\
Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
Number of host halos: 21\\
Planes: yes\\
co-rotation: yes\\
note: \\
}

\item{Buck et al 2016 "Simulated $\Lambda$CDM analogues of the thin Plane of Satellites
around the Andromeda galaxy are not kinematically
coherent structures":\\
They use zoom in cosmological simulation of high concentration haloes to study the dynamics of the satellite population.\\
Conclusion: "Thus we conclude that the line-of-sight velocity is not well suited as a proxy for the kinematical coherence of the plane.
Analysis of the kinematics of our planes shows a fraction of 30$\%$ chance aligned
satellites. Tracking the satellites in the plane back in time reveals that these planes
are a transient feature and not kinematically coherent as would appear at first sight.
Thus we expect some of the satellites in the plane around Andromeda to have high
velocities perpendicular to the plane."\\
Simulation: 21 high resolution "zoom-in" Dark Matter only simulations. Andromeda-mass haloes in the mass range
(7,4$\times 10^{11} < M_{200}M_\odot < 2,2 \times 10^{12}$).\\
Gas: NO\\
Resolution : resolve substructure down to $10^7 h^{-1}M\odot$\\
Number of host halos: 21\\
Planes: yes\\
co-rotation: yes (when they look at angular momenta they find MW like co-rotation. When they look at line-of-sight velocities they find that 30$\%$ of the satellites are not co-rotating despited the apparent co-rotation form the line-of-sight velocity).\\
note: \\
}

%\item{ :\\
%Conclusion: \\
%Simulation: \\
%Gas: \\
%Resolution : \\
%Number of host halos: \\
%Planes: \\
%co-rotation: \\
%note: \\
%}

\end{itemize}
